Sparse Word Embeddings for Multi-domain Machine Translation

### 2019-05-13 2019/emnlp/sparse.tex
fix a glitch in abstract

\fyDone{s/naacl/EMNLP/g}
\fyTodo{Too long, selfcontained, noref, rewrite}
\begin{abstract}help train
  Supervised machine translation is well suited to the situation where the training and testing data are from the same domain. When this is not the case, \emph{domain adaptation} techniques are needed to ensure that the knowledge of the source, out-of-domain data, generalizes properly to the target, in domain, texts. We study a related setting, multi-domain adaptation, where the number of domains is potentially large, and where adapting separately to each woud waste training resources. Our proposal transposes to neural machine translation the feature expansion technique of (Daum\'e, 2007), and isolate domain-agnostic from domain-specific lexical representations, while sharing the rest of the architecture across domains. Our experiments use two standard architecture and two language pairs: they show that our approach, while remaining simple and computationally unexpensive, outperforms several strong baselines, and delivers a multi-domain system that can sucessfully process heterogeneous input sentences.

>>>>

\fyDone{s/naacl/EMNLP/g}
\fyDone{Too long, selfcontained, noref, rewrite}
\begin{abstract}
  Supervised machine translation is well suited to the case where the train and test data are from the same domain. When this is not the case, \emph{domain adaptation} techniques help ensure that the knowledge of the out-of-domain data generalizes properly to target domain texts. We study a related setting, multi-domain adaptation, where the number of domains is potentially large, and where adapting separately to each domain woud waste training resources. Our proposal transposes to neural machine translation the feature expansion technique of (Daum\'e, 2007), and isolates domain-agnostic from domain-specific lexical representations, while sharing the rest of the network across domains. Our experiments use two architectures and two language pairs: they show that our approach, while remaining simple and computationally unexpensive, outperforms several strong baselines, and delivers a multi-domain system that can sucessfully process heterogeneous input sentences.
